Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-06 paper.tex
Added some sections to my paper.

% This is a sample document using the University of Minnesota, Morris, Computer Science
% Senior Seminar modification of the ACM sig-alternate style to generate a simple annotated
% bibliography. The idea is that this document is fairly short, consisting of a brief description
% of your sources and how you intend to use them (or not). Most of the ``content'' of the
% generated document comes from the bibliography file, including the notes field which will
% provide the annotations.

% See https://github.com/UMM-CSci/Senior_seminar_templates for more info and to make
% suggestions and corrections.

\documentclass{sig-alternate}

@@

\maketitle

\begin{abstract}
This paper discusses the use of artificial intelligence in intrusion detection systems.
\end{abstract}

@@

\terms{Intrusion detection}

\keywords{Genetic algorithms, Fuzzy logic}

\section{Introduction}
I will be looking at how genetic algorithms and fuzzy logic are used to train intrusion detection systems about possible threats.

I plan to use the following sources:
\begin{itemize}
\item I expect~\cite{DBLP:journals/corr/abs-1204-1336} and~\cite{6496342} to be two of my main sources.
\item I may use~\cite{bc1_ecindm} for my third source or for background. 
\item I'll use~\cite{Liao201316, DBLP:journals/corr/abs-1204-6416, bapuji2012soft} as background. 
\end{itemize}

I won't be using~\cite{Sangkatsanee20112227}, because it doesn't talk about genetic algorithms or fuzzy logic.

% The following two commands are all you need to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
% annotated_bibliography.bib is the name of the BibTex file containing 
% all the bibliography entries for this example. Note that you *don't* include the .bib ending
% in the \bibliography command.
\bibliography{annotated_bibliography}

% You must have a ".bib" file and remember to run:
%     pdflatex bibtex pdflatex pdflatex
% in order to see all the citation references correctly.

>>>>

\documentclass{sig-alternate}
\usepackage{color}

%%%% User-defined macros
\newcommand{\lam}{\lambda}
\newcommand{\mycomment}[1]{\textcolor{red}{#1}}
%%%%% Uncomment the following line and comment out the previous one
%%%%% to remove all comments
%%%%% NOTE: comments still occupy a line even if invisible;
%%%%% Don't write them as a separate paragraph
%\newcommand{\mycomment}[1]{}

@@

\maketitle
\begin{abstract}

\end{abstract}

@@

%\terms{Delphi theory}

\keywords{Intrusion detection, genetic algorithm, fuzzy logic}

\section{Introduction}

\section{Background}

\subsection{Types of Intrusion Detection Systems}

\subsection{Types of Networking Attacks}

\subsection{Detection Methodologies}

\subsection{Genetic Algorithm}

\subsection{Fuzzy Logic}

\subsection{KDD99 Data Set}

\section{Fuzzy Genetic Algorithm Implementation}

\subsection{RLD09 Data Set}

\subsection{Algorithm Overview}

\subsection{Experimental Design and Results}

\section{Genetic Algorithm Implementation}

\subsection{Algorithm Overview}

\subsection{Experimental Design and Results}

\section{Conclusions}

\section{Acknowledgments}

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
% sample_paper.bib is the name of the BibTex file containing the
% bibliography entries. Note that you *don't* include the .bib ending here.
\bibliography{annotated_bibliography}  
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
